# `r fontawesome::fa("brain", fill = "pink")` Resources. {#sec-resources}

Academic resources encompass a wide range of materials, tools, and sources of information specifically designed to support and enhance learning, research, and scholarly pursuits in an academic setting. These resources play a crucial role in facilitating knowledge acquisition, promoting critical thinking, and advancing scholarly activities within the academic community.

<!-- ## `r fontawesome::fa("toolbox")` Learning resources. -->

Here is a list and description of the available resources to help you learn the subject. My advice is to utilize as many resources as possible, as they will enable you to grasp the subject matter and develop the necessary professional competences.

**Professor.** I have extensive experience as an academic and researcher, along with numerous postgraduate studies. I am willing to assist you in better understanding the course topics. If you need any help, feel free to contact me <tt>`<martin.lozano@udem.edu>`</tt> and follow my advice.

Please watch the video about professors:

```{r echo=FALSE}
embed_url("https://youtu.be/IzG85NDDo1Q")
```

**Groups.** Exams and homework assignments (see @sec-activities) are group-based, so your team will be an important part of your academic support throughout the course.

<a id="sec-gp"></a>

::: {.callout-important}
### Groups policies.

1. Group size and formation: Groups may include up to four students. Group activities may be completed by one, two, three, or four students. Students form groups at the beginning of the semester.
1. Switching groups: A student may switch groups only with written consent from both (a) the group they are leaving and (b) the group they are joining. This requires at least two emails, one from each group, and each email must CC all members of both groups and me. I must authorize the change to confirm that no group exceeds four members. Requests must be submitted no later than one week before the next exam or the final exam. Requests received after this deadline will be rejected.
1. Expelling a member: Expulsion is an available option for all teams. To proceed, the team must provide a previously signed team agreement that defines expectations (e.g., communication, deadlines, contribution standards) and evidence showing the member did not meet them. Without a signed agreement and clear evidence, I cannot authorize the expulsion.
1. Unauthorized changes are not allowed: Students may not change groups or expel a member on their own. Any group change or expulsion is official only after it follows the policies above and receives my authorization. Until then, the original group membership remains in effect for all graded activities.
1. Team agreements: I strongly advise each team to create written rules and expectations at the start of the semester (e.g., communication norms, task division, deadlines, and how contributions will be documented). These agreements are managed within the team; I do not intervene in internal team arrangements. Because coevaluation has a significant impact on individual marks in group work, documenting contributions and expectations from the start is essential.
:::

**Class sessions.** During our class sessions, we will explain and discuss specific topics, address questions, review your study progress, and occasionally conduct brief activities. Please keep in mind that the time available during class sessions is limited, and we may not be able to cover every topic in full detail. To ensure comprehensive coverage, we will utilize other resources and learning activities. It is expected that you attend on time, actively participate, and engage in our discussions. I recommend using your computer during the sessions as you may need to access an IDE, view the PDF textbook, or refer to your own homework.

For Zoom sessions, you have the option to keep your camera either on or off, as we will often be sharing the screen during class, or you will be doing an activity. To provide convenience, unless otherwise specified, class Zoom sessions will be recorded and made accessible to you. Please note that occasional internet service disruptions during class sessions are a risk we all face. The Zoom link to join the class can be found in Blackboard and in @sec-schedule.

<a id="sec-tp"></a>

::: {.callout-important}
### Tardiness policies.

1. Face-to-face tardiness: In face-to-face classes, two tardies count as one absence. Tardies accumulate over the course of the semester. A tardy is recorded if the student arrives immediately after attendance is taken and remains for the rest of the class. If a student is marked as present or tardy, this can be changed to an absence if they leave the classroom or do not stay until the end of the class.
1. Online attendance: In online classes, there is no tardiness policy. Attendance is based on the Zoom activity log (minutes connected). Each session results in either an attendance or an absence. Students must be connected for at least 90% of the class to be marked present. You must join using your own Zoom login credentials to verify identity and correctly attribute attendance.
1. Online connectivity: In online classes, connectivity problems do not excuse absences. Attendance is determined solely by the Zoom activity log (time connected). Students are responsible for ensuring reliable access and joining with their own Zoom account.
1. Zoom sessions in a face-to-face course: In face-to-face classes, we usually hold a few Zoom sessions during the semester (see @sec-schedule for details). During these sessions, the policy is the same as in online classes.
1. Weather-related emergency switch to Zoom: In face-to-face classes, it is possible that an occasional session may be moved to Zoom due to extreme weather conditions that cannot be reasonably anticipated. If this happens, I will notify students by email with updated instructions.
1. One-time Zoom exception for face-to-face sessions: In face-to-face classes, students may attend a designated face-to-face session via Zoom once per semester as an exception. If this applies to you, notify me by email. If it happens a second time, the student may still attend via Zoom, but I will record an absence in accordance with current university regulations.
1. Maximum absences: With respect to the maximum absences policy, we will adhere to the current university regulations.
:::

Please watch the following video for a valuable recommendation from Prof. Fleisch, which is applicable to both online and face-to-face sessions:

```{r echo=FALSE}
embed_url("https://youtu.be/KX-sg1HXAws")
```

<!-- **Audio files (if available).** I explain part of the course material with my *sweet melodic* voice. Some students might have difficulties at understanding the required readings and I believe these mp3 audio files are useful to better understand some topics. It is compulsory to listen to them before the class session. Please note that not all the course material is discussed in audio files, for this reason you are not supposed to listen to audio files and ignore the rest of the course material, all resources complement each other. Audio files are not listed in the course calendar, but it will be easy for you to identify which audio file corresponds to each course topic. -->

**Review sessions.** We have review sessions for assignments and exams, which take place before the homework assignment submission deadline and prior to the exams. These sessions provide a great opportunity to ask questions and enhance your chances of achieving higher marks in both assignments and exams. I usually avoid to discuss new material during these review sessions.

See some recommendations about review sessions:

```{r echo=FALSE}
embed_url("https://youtu.be/XoHx_UIgtt0")
```

**Discussion forums.** There are three discussion forums available for us to interact and engage with one another. Each forum corresponds to a different part of the course: the first, second, and third part. The benefit of the discussion forums is that everyone can track the progression of discussions and actively participate. The logical flow of ideas remains recorded, allowing you to receive my feedback and comments. Since our class sessions have limited time, we may occasionally utilize the discussion forums.

**Email.** You are welcome to contact me via email at any time: <tt>`<martin.lozano@udem.edu>`</tt>. I also send group emails containing important information, so ensure that my email address is not marked as spam. If there is ever a delay in my response to an email or any other request, please feel free to insist and kindly remind me.

**Meetings.** Whether it is face-to-face or virtual learning, we can schedule 30-minute Zoom online meetings if you require additional assistance or have any other issues you would like to discuss with me. These meetings can be arranged either individually or in groups. Simply send an email to <tt>`<martin.lozano@udem.edu>`</tt> to inquire about my availability. I ask that meetings be arranged by email so that I have written evidence of the arrangement and the necessary time to check my schedule before confirming available hours. If my initial availability does not work for you, feel free to let me know, I can offer alternative times until we find a mutually convenient slot. If you need more time, we can arrange for additional meetings or extend the duration as needed. Here is the Zoom link for meetings: [https://us02web.zoom.us/j/9209945512](https://us02web.zoom.us/j/9209945512). The student or the group may request that the Zoom meeting be recorded, and I can share the recording with them for future reference. For the class session Zoom link, refer to the course calendar: @sec-schedule.

**DataCamp** DataCamp is an online learning platform focused on data science and analytics. It offers interactive courses in Python, R, SQL, and other tools commonly used in data analysis, machine learning, and statistics. Users learn by writing and running code directly in the browser, with instant feedback and guided exercises. You have free and full access as my student this semester.

<a id="sec-dcp"></a>

::: {.callout-important}
### DataCamp policies.

*This section is the official submission policy for all graded activities (homework and exams). If any other section summarizes these rules, this section prevails.*

1. Platform and backup: We rely on DataLab (DataCamp) for completing homework assignments and exams (see @sec-activities). DataLab is the official course workspace: you will work there, and I will access your work there to evaluate it. In this course, there is typically no separate “upload-and-submit” step; instead, you are responsible for ensuring your work is saved and located correctly in DataLab for grading. Because these platforms may experience occasional downtime, you must have RStudio installed on your local computer as a backup so you can continue working in an emergency.
1. Required format and environment: All homework assignments and exams must be completed and made available for grading within DataLab as Jupyter notebooks (<tt>`.ipynb`</tt>). Although DataLab may allow uploads in formats such as PDF or MS Word, those formats are not acceptable for evaluated homework or exams in this course. You must complete your work directly in the provided Jupyter notebook environment to ensure consistency and proper evaluation.
1. “Submissions” folder requirement: In DataLab, students often create multiple documents and folders. For convenience, I have created a folder called “submissions” in your group workspace. You must place the notebooks I need to evaluate (assignments and exams) in this folder. Do not rename the folder.
1. Correct location is required: Because DataLab and Jupyter notebooks may be new tools for some students, you must be careful when providing work for grading. All activities must be placed in the correct group workspace (identified by the group name) and inside the “submissions” folder. Work placed in the wrong workspace or folder—even if completed—will be treated as not submitted. No exceptions will be made for work located in incorrect folders or workspaces.
1. After completing your final exam $E_F$, you will no longer have editor access to DataLab. Therefore, I suggest that you create a backup of any documents you wish to keep.
:::

**Book.** The book (or books) is one of the main pillars of this course. In my experience, learning primarily occurs through reading and then reinforcing the concepts through practical application, although there are various other activities included in this course. The authors of the book are esteemed experts in their respective fields: John C. Hull from [University of Toronto](https://www.utoronto.ca/); Frank Fabozzi from [Johns Hopkins Carey Business School](https://carey.jhu.edu/); Richard A. Brealey from [London Business School](https://www.london.edu/); Stewart C. Myers from [Sloan School of Management, Massachusetts Institute of Technology](https://mitsloan.mit.edu/); Franklin Allen from [Imperial College London](https://www.imperial.ac.uk/); Rob J. Hyndman and George Athanasopoulos from [Monash University](https://www.monash.edu/); ad Eugene F. Brigham and Joel F. Houston from [University of Florida](https://www.ufl.edu/). These books are not only suitable for intermediate and advanced undergraduate degrees but also for first-year master's degrees. I prefer using the original versions of the books rather than translations because, in my experience, the translations may not always match the quality of the original English version and, in some cases, may not be available.

**Tutorials.** I have created a series of specialized online tutorials that provide step-by-step instructions on implementing various topics and estimating financial and economic models using data. These tutorials aim to help you bridge the gap between the theoretical concepts presented in the textbook and the practical implementation in R code. This approach, often referred to as literate programming, allows for a seamless transition. You can access my tutorials in my GitHub public repository [https://github.com/mlozanoqf](https://github.com/mlozanoqf), or more easily via GitHub Pages: [Quantitative Finance with R](https://mlozanoqf.github.io/).

**Ah, ya entendí.** I have created a series of specialized video tutorials that provide step-by-step instructions on implementing various topics and estimating financial and economic models using data. You can access my YouTube channel here: [Ah, ya entendí](https://www.youtube.com/@ahyaentendi).

**Others**. All learning resources described above represent a good resource for your own study of the course material. There are plenty of Internet resources that you will have to use, from databases, [YouTube](https://www.youtube.com/) videos, [GitHub](https://github.com/) public repositories, specialized programming blogs, AI tools, books, electronic books, etc. See the resource list at the end of this document for further details. You are encouraged to read articles, reports and news on your own to enhance and expand your understanding about how theoretical concepts relate with current real-life events. [The Economist](https://www.economist.com/), [The Financial Times](https://www.ft.com/), [The Guardian](https://www.theguardian.com/), [The Wall Street Journal](https://www.wsj.com/), [MarketWatch](https://www.marketwatch.com/), [Reuters](https://www.reuters.com/), [Bloomberg](https://www.bloomberg.com/), [Bureau of Economic Analysis](https://www.bea.gov/), [Banxico](https://www.banxico.org.mx/), [Project Syndicate](https://www.project-syndicate.org/), [The New York Times](https://www.nytimes.com/), [El Financiero](https://www.elfinanciero.com.mx/) (México), [El Confidencial](https://www.elconfidencial.com/) (Spain), [OECD](https://www.oecd.org/), are a good way to grasp contemporary insights related with this course. Other references to support your learning process include economic and financial reports from private banks such as Banamex and BBVA, and think tanks websites such as [The Mexico Institute](https://www.wilsoncenter.org/program/mexico-institute), [México cómo vamos](https://mexicocomovamos.mx/), [CIDAC](http://cidac.org/), [IMCO](https://imco.org.mx/), [COMEXI](https://www.consejomexicano.org/), among many others. My advice in this respect is rather simple: *the more you read the more you learn*.

**Further support.** `r fontawesome::fa("hands-helping")` 

In case you have any concern, any question about the course contents, or if you are having trouble understanding the course material, you have to contact me as soon as possible. This is your own responsibility starting from day 1. We can arrange an online meeting, or we can solve your questions or concerns by email, whatever is best. In case you are having a poor academic performance and you are genuinely interested to improve, my best advice is to contact me during the lecture period, not after the last session of the semester, and we can discuss specific strategies that can potentially help you to get higher marks and reduce the risk of failing the course. The point here is that you have to know that I can help you to improve your academic performance during the semester only if you are truly interested. If you would like to improve your marks at a later stage, or after the final exam, then I am afraid I can do nothing for you, but I can do a lot during the semester. Please email me in case you would like to arrange an appointment, my full contact details are at the beginning of this syllabus. The email is definitely the best way to initially approach me.

In case you get a low mark in one activity or you get difficulties at some specific topic you should take immediate actions in order to quickly revert this. I am not planning to relax the marking criterion so what you have to do is to improve your own quality standards in order to pass given my marking standards and my expectations about your academic performance. You are free to contact me in case you need assistance about specific strategies to improve your academic performance.

I recommend that you do not get disappointed, angry or sad if you get a low mark. There is no need for that because getting one low mark is not determinant to fail the course. Please see the evaluation method to verify how the final grade is computed and you will be amazed in a positive way. Also, I do not recommend you to get frustrated if you receive an unexpected low mark or an unexpected negative feedback about your work or your answers. The mechanics here are very simple: *in order to improve, understand and learn, you need to know what you did well, what you did wrong, and try again until you do well without getting desperate or frustrated in the process*. In short, avoid negative feelings as these might lead to further frustration. Nobody wants to hurt you, we all want you to learn in a favorable environment. You have overcome challenges before, so avoid the dark side `r fontawesome::fa("ghost")`. On the contrary, you should rather work harder to meet the course standards. We are not in conflict, in fact we are collaborating. According to my experience, students who sadly fail this course ignore or forget these recommendations.

As a student, you may have different responsibilities. You are probably working, you might have family commitments, other courses, unexpected workload, troubles, and other diverse duties. All these may affect your academic performance at some time. My view here is that you are expected to do well in all aspects of your life and you will have to manage your time effectively and be productive. I hope you can allocate your time in such a way that you can pass this course and do well in the rest of your personal activities. Sometimes the workload is so intense that you have to evaluate whether you need to drop an activity to do well in the rest and keep you healthy, physically and mentally. If you find yourself overwhelmed by your personal troubles, workload and responsibilities, please ask for help, the university has professionals that can help you with this. If you have personal problems I can hear you and if I am unable to guide you properly, we can ask for professional help. Keep this in mind, we all care about your health, and health is far more important than a job, a course, and the university.

This is a video from The University of Arizona Global Campus about How to Manage College Stress.

```{r echo=FALSE}
embed_url("https://youtu.be/_2BFj-k__s0?si=B5pTS3Zs0X1EJIUF")
```

We all know that good grades do not necessarily make you a good person or a good professional. One could have difficulties at school but have such a good professional network, or an impressive ability to do business, or an impressive entrepreneurship spirit. However, grades are still quite useful to assess how well you are at meeting some academic standards and how well you manage to understand the relevant topics in your area of expertise. It is more important to be a good person than a good professional, and the graded activities are specifically designed to partially evaluate your technical abilities as a professional. Then, we all assume that you are a good person, and the course activities will help us to evaluate some of the required skills and competences as professionals. Having said that, I hope you can achieve high grades in this course.

<!-- Easter egg. The first three students who read this and send a photo of a cat wearing glasses to my email before August 20 will receive +5 marks on their next exam. If using a real cat, please ensure the animal is not harmed or distressed in any way. -->

In sum, I expect the best academic performance you can achieve, not the average, and definitely not the minimum. This should not be a surprise since you are studying at one of the most prestigious private universities in the country (we belong to a business school with AACSB and AMBA accreditation). If you succeed at delivering your best performance in this course, and I believe you can, then you might be in a better position to eventually tackle business problems including the most interesting and valuable ones which includes those that do not exist yet. I am sure you have done some extraordinary things in the past, you have overcome very hard challenges, so take this course just as another opportunity to unleash your full potential and show me how committed you are with your academic professional training. 

I strongly believe you can learn anything just as this video from Khan Academy indicates:

```{r echo=FALSE}
embed_url("https://youtu.be/JC82Il2cjqA")
```

Most of my previous recommendations in this subsection are for those who are having difficulties with the course. If you are doing fine, then good for you `r fontawesome::fa("thumbs-up")`, try to enjoy the learning process as much as you can. My commitment is that you will have all the support and resources you need to pass the course during the semester; you only have to take them or ask for them during the lecture period, not after the last course session, and follow all my recommendations in this syllabus.


